Comparing R packages for calculation of persistent homology

### 2020-02-20 tdabench-paper/tdabench.Rmd
fixed indentation/newlines

\begin{figure}
  \centering
  \includegraphics[height=2.5in]{../Figures/Final_Figures/fig1.png}
  \caption{\textbf{Calculating persistent homology of a torus with three TDA libraries.}
  Average runtime (mean $\pm$ SD) for each TDA library (denoted by color) is plotted against point cloud size.
  Homological features up to 2 dimensions were calculated.
  Time complexity follows a power law for all three libraries (see GitHub repo for regression details).
  Although the libraries have similar runtimes for smaller point clouds, Dionysus has a clear disadvantage when the number of points exceeds 100.
  When the number of points exceeds 200, Ripser has a clear advantage over GUDHI, which maintains its advantage over Dionysus.
  }
\label{fig:tor}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[height=2.5in]{../Figures/Final_Figures/fig1.png}
  \caption{
    \textbf{Calculating persistent homology of a torus with three TDA libraries.}
    Average runtime (mean $\pm$ SD) for each TDA library (denoted by color) is plotted against point cloud size.
    Homological features up to 2 dimensions were calculated.
    Time complexity follows a power law for all three libraries (see GitHub repo for regression details).
    Although the libraries have similar runtimes for smaller point clouds, Dionysus has a clear disadvantage when the number of points exceeds 100.
    When the number of points exceeds 200, Ripser has a clear advantage over GUDHI, which maintains its advantage over Dionysus.
  }
\label{fig:tor}
\end{figure}
